---
title: 'Project 2nd attempt'
author: "Aashna Rungta"

date: "November 14, 2021"
output:
  html_document: default
  header-includes: \usepackage{color}
fontsize: 12pt
margin: 1in
---


```{r setup, echo=FALSE, message=F, warning=F}

    rm(list = ls())
#saving file to R files folder
setwd("/Users/aashnarungta/SCU/EconometricswithR/R_files/Project")

### Load the packages 
    library(doBy)
    library(dplyr)
    library(foreign)
    library(ggplot2)
    library(knitr)
    library(lmtest)
    library(readstata13)
    library(sandwich)
    library(stargazer)
    library(AER)
    library(gdata)
    library(wooldridge)
    library(openintro)
    library(tidyr)
    library(tidyverse)

cse=function(reg) {
    rob=sqrt(diag(vcovHC(reg, type="HC1")))
    return(rob)
    }
    
```



```{r data, echo=FALSE, message=F, warning=FALSE, include=FALSE}
#loading the data
student=read.csv("student-mat.csv", header=T, sep=",")

```


```{r simple, echo=FALSE, message=F, warning=FALSE, comment=""}

student <- student %>% rowwise() %>%
  mutate(Grades = sum(c_across(G1:G3)))


ggplot(student, aes(x=Dalc, y=Grades)) + geom_point(col="blue") +
        labs(title = "Daily Alc consumption on grades", x = "Daily Alcohol Consumption", y = "Grades", hjust=1, vjust=1) +
        stat_smooth(method=lm, col = "red", se=FALSE)


ggplot(student, aes(x=Walc, y=Grades)) + geom_point(col="blue") +
        labs(title = "Weekly Alc consumption on grades", x = "Weekly Alcohol Consumption", y = "Grades", hjust=1, vjust=1) +
        stat_smooth(method=lm, col = "red", se=FALSE)

```


```{r multiple, echo=FALSE, message=F, warning=FALSE, comment=""}

# Inserting scatterplot graphs of Looks on other variables.

Grades_dalc = lm(Grades ~ Dalc, data = student)
Grades_abs = lm(Grades ~ Dalc + absences, data = student)
Grades_health = lm(Grades ~ Dalc + absences + health, data = student)
Grades_activities = lm(Grades ~ Dalc + absences + health + activities, data = student)
Grades_studytime = lm(Grades ~ Dalc + absences + health+ activities+ studytime, data = student)
Grades_schoolsup = lm(Grades ~ Dalc + absences + health+ activities + studytime + schoolsup, data = student)

stargazer(Grades_dalc, Grades_abs, Grades_health, Grades_activities, Grades_studytime, Grades_schoolsup, se=list(cse(Grades_dalc), cse(Grades_abs), cse(Grades_health), cse(Grades_activities), cse(Grades_studytime), cse(Grades_schoolsup)), title="Grades against all else", type="text", df=FALSE, digits=3)

absence_Dalc = lm(absences ~ Dalc, data = student)
absence_health = lm(absences ~ Dalc + health, data = student)
absence_activities = lm(absences ~ Dalc + health + activities, data = student)
absence_studytime= lm(absences ~ Dalc + health+ activities+ studytime, data = student)
absence_schoolsup = lm(absences ~ Dalc + health+ activities + studytime + schoolsup, data = student)

stargazer(absence_Dalc, absence_health, absence_activities, absence_studytime, absence_schoolsup, se=list(cse(absence_Dalc), cse(absence_health), cse(absence_activities), cse(absence_studytime), cse(absence_schoolsup)), title="Absence against all else", type="text", df=FALSE, digits=3)

# Grades_absence = lm(Grades ~ absences, data = student)
# 
# stargazer(Grades_absence, se=list(cse(Grades_absence)), title="Absense against Grades", type="text", df=FALSE, digits=3)

# Grades_studytime = lm(Grades ~ studytime, data = student)
# 
# stargazer(Grades_studytime, se=list(cse(Grades_studytime)), title="Grades against study time", type="text", df=FALSE, digits=3)

```

## Observations:

#### Does alcohol consumption affect school grades?

-Simple regression is statistically significant at 10%

-coefficient = 0.903

-Adjusted R2 is highest with all the control variables (but still very low.)

-But the only other statistically significant variables are studytime and whether or not the kid is getting supplementary help from school

-Seems like absences/health doesn't affect grades much at all.



#### Does alcohol consumption affect absences?

-based on coefficient, not really.

-but the almost 1 coefficient is always statistically significant

-Adjusted R2 is highest when it's a simple regression, without any control variables.

#### My recommendation: If we had to choose between these two regressions, then choose the first one (Dalc on Grades) (But even that's not very exciting)

