---
title: 'Project 1st attempt'
author: "Udisha"

date: "November 17, 2021"
output:
  html_document: default
  header-includes: \usepackage{color}
fontsize: 12pt
margin: 1in
---


```{r setup, echo=FALSE, message=F, warning=F}

    rm(list = ls())
#saving file to R files folder
setwd("~/Downloads/Fall21/2509 ECON/Final Project")

### Load the packages 
    library(doBy)
    library(dplyr)
    library(foreign)
    library(ggplot2)
    library(knitr)
    library(lmtest)
    library(readstata13)
    library(sandwich)
    library(stargazer)
    library(AER)
    library(gdata)
    library(wooldridge)
    library(openintro)
    library(tidyr)
    library(tidyverse)

cse=function(reg) {
    rob=sqrt(diag(vcovHC(reg, type="HC1")))
    return(rob)
    }
    
```



```{r data, echo=FALSE, message=F, warning=FALSE, include=FALSE}
#loading the data
student=read.csv("student-mat.csv", header=T, sep=",")
student$urban <- ifelse(student$address == 'U', 1, 0)
student$pstat <- ifelse(student$Pstatus == 'A', 1, 0)

```


```{r simple, echo=FALSE, message=F, warning=FALSE, comment=""}

student <- student %>% rowwise() %>%
  mutate(Grades = sum(c_across(G1:G3)))


ggplot(student, aes(x=Dalc, y=Grades)) + geom_point(col="blue") +
        labs(title = "Daily Alc consumption on grades", x = "Daily Alcohol Consumption", y = "Grades", hjust=1, vjust=1) +
        stat_smooth(method=lm, col = "red", se=FALSE)


ggplot(student, aes(x=Walc, y=Grades)) + geom_point(col="blue") +
        labs(title = "Weekly Alc consumption on grades", x = "Weekly Alcohol Consumption", y = "Grades", hjust=1, vjust=1) +
        stat_smooth(method=lm, col = "red", se=FALSE)

```


```{r multiple, echo=FALSE, message=F, warning=FALSE, comment=""}

# Inserting scatterplot graphs of Looks on other variables.

reg1 = lm(Grades ~ Dalc, data = student)
reg2 = lm(Grades ~ Dalc + absences, data = student)
reg3 = lm(Grades ~ Dalc + absences + schoolsup , data = student)
reg4 = lm(Grades ~ Dalc + absences + schoolsup+ internet, data = student)
reg5 = lm(Grades ~ Dalc + absences + schoolsup+  internet + studytime, data = student)
reg6 = lm(Grades ~ Dalc + absences + schoolsup + internet + studytime + traveltime , data = student)

stargazer(reg1, reg2, reg3, reg4, reg5, reg6, se=list(cse(reg1), cse(reg2), cse(reg3), cse(reg4), cse(reg5), cse(reg6)), title="Grades against all else", type="text", df=FALSE, digits=3)

romantic1 = lm(Grades ~ romantic, data = student)
romantic2 = lm(Grades ~ romantic + studytime , data = student)
#romantic3 = lm(Grades ~ romantic + famrel + Pstatus, data = student)
romantic4 = lm(Grades ~ romantic + studytime+ goout, data = student)
romantic5 = lm(Grades ~ romantic + studytime + goout + age , data = student)
romantic6 = lm(Grades ~ romantic + studytime + goout + age +  address, data = student)
romantic7 = lm(Grades ~ romantic + studytime + goout + age + address + activities, data = student)


stargazer(romantic1, romantic2, romantic4, romantic5, romantic6, romantic7, se=list(cse(romantic1), cse(romantic2), cse(romantic4), cse(romantic5), cse(romantic6), cse(romantic7)), title="Romantic against all else", type="text", df=FALSE, digits=3)



```

Effect of alcohol consumption on grades:

We first run the regression model 1 with grades on daily alcohol consumption and see it is significant at 10% level. Since the model is a simple linear model, we suspect omitted variable bias and add other regressors to analyse the best baseline specification model.

As expected, we saw the fit of the model go up from 0.3% to 4.6% after adding other regressors. 

We want to study if alcohol consumption affects the grades of a student. From the star table, we notice there's a negative correlation but it is not statistically significant at standard confidence levels. 

From the regression table, we see absence from school too does not have a significant effect on the grades.
However, we notice the extra educational support has a very significant effect on grades with a 1% level.
Having internet also positively affects the grades with a significance level of 10%.
We noticed that study time positively affects the grades and is statistically significant at 5% whereas the travel time affects the grades negatively and is significant at 5% level.

To conclude, we reject our null hypothesis of alcohol consumption affecting grades. 


